Dirac neutrino mass generation from Majorana messenger

### 2019-09-18 draft.tex
pt

\usepackage{comment}
\includecomment{details}
\specialcomment{details}
{\begingroup}{\endgroup}
\excludecomment{details}
%\PreviewEnvironment{details}
%%%%%%
%Custom definitions
\usepackage{tikz}
\newcommand{\ReportNumbers}[1]{%
\begin{tikzpicture}[overlay, remember picture]
\path (current page.north east) ++(-1,-1) node[below left] {#1};
\end{tikzpicture}
}
%%%%%%%%%%%%%%%TITLE PAGE

@@

\author{First Author\footnote{\href{mailto:first@author}{first@author}},
Second Author\footnote{\href{mailto:second@author}{second@author}}\\
\textit{\small  First Institute}\\
[4mm]
Third Author\footnote{\href{mailto:third@author }{third@author}}\\
\textit{\small Second Institute}
}
\date{\small Month NN, YYYY}
\begin{document}
\maketitle
\ReportNumbers{XXX-XXX}

>>>>

\usepackage{comment}
\includecomment{details}
\specialcomment{details}
{\begingroup}{\endgroup}
\excludecomment{details}
%\PreviewEnvironment{details}
%%%%%%
%Custom definitions
\usepackage{tikz}
\newcommand{\ReportNumbers}[1]{%
\begin{tikzpicture}[overlay, remember picture]
\path (current page.north east) ++(-1,-1) node[below left] {#1};
\end{tikzpicture}
}
%%%%%%
% \newcommand{\UPTC}{Escuela de Física, Universidad Pedagógica y Tecnológica de Colombia,\\
% Avenida Central del Norte \# 39-115, Tunja, Colombia}
\newcommand{\UdeA}{}
%%%%%%%%%%%%%%%TITLE PAGE

@@

\author{Julian Calle${}^1$\footnote{\href{mailto:julian.callem@udea.edu.co}{julian.callem@udea.edu.co}},
  Diego Restrepo${}^{1,2}$\footnote{\href{mailto:restrepo@udea.edu.co}{restrepo@udea.edu.co}}, and Óscar Zapata${}^1$\footnote{\href{mailto:oalberto.zapata@udea.edu.co }{oalberto.zapata@udea.edu.co}}\\
[2mm]  
\textit{\small ${}^1$Instituto de Física,
  Universidad de Antioquia,
}\\
\textit{\small   Calle 70 \# 52-21, Apartado Aéreo 1226, Medellín, Colombia.}\\
[2mm]
\textit{\small ${}^2$
International Institute of Physics, Universidade Federal do Rio Grande do Norte,
}\\
\textit{\small Campus Universitario, Lagoa Nova, Natal-RN 59078-970, Brazil. }
}
\date{\small September DD, 2019}
\begin{document}
\maketitle
\ReportNumbers{IIPDM-2019}
